Environment affects specialisation of plants and pollinators

### 2019-12-01 paper/manuscript.Rmd
Using 95% CI for slopes and intercepts

>>>>

```{r}
loadd(random_slope_intercepts)
# random_slope_intercepts <- readRDS("rsi.rds")

species_types <- random_slope_intercepts %>%
  # dplyr::rename_all(stringr::str_replace, "Q75", "Q97.5") %>%
  # dplyr::rename_all(stringr::str_replace, "Q25", "Q2.5") %>%
  # = Q75, Q2.5 = Q25) %>%
  dplyr::mutate(intercept_sig = dplyr::case_when(Intercept_Q2.5 > 0 ~ "positive", Intercept_Q97.5 < 0 ~ "negative", TRUE ~ "indeterminate"), 
                slope_sig = dplyr::case_when(scaled_suitability_Q2.5 > 0 ~ "positive", scaled_suitability_Q97.5 < 0 ~ "negative", TRUE ~ "indeterminate"), 
                int_slo = interaction(intercept_sig, slope_sig), 
                int_slo = dplyr::case_when(int_slo == "indeterminate.indeterminate" ~ "neither generalist or specialist", int_slo == "positive.indeterminate" ~ "true generalist", int_slo == "negative.indeterminate" ~ "true specialist", int_slo %in% c("positive.positive", "negative.negative") ~ "flexible species", TRUE ~ "flexible species") ) %>%
  dplyr::mutate(int_slo = forcats::fct_infreq(int_slo))

species_types %>%
  dplyr::count(int_slo, guild) %>%
  tidyr::spread(guild, n)

  # dplyr::filter(intercept_sig != "indeterminate") %>%
  # table(slope_sig, intercept_sig)

library(ggplot2)
species_types %>%  # 
  ggplot(aes(x = int_slo, fill = guild)) +
  geom_bar() +
  coord_flip()
```
